Proof of concept

### 2022-12-21 docs/src/paper/data_preprocessing/_real_world_data.qmd
I just don't know why this isn't working for cat data

```{julia}
df = CSV.read(joinpath(data_path, "raw/cal_housing.csv"), DataFrame)
# # Features:
# X = Matrix(df[:,Not(:target)])
# dt = StatsBase.fit(ZScoreTransform, X, dims=1)
# StatsBase.transform!(dt, X)
# df = DataFrame(X,:auto)
# Target:
y = df.target
y = Float64.(y .>= median(y)); # binary target (positive outcome)
# Data:
df.target = y
```

@@

@@

```{julia}
X = Matrix(df_balanced[:,Not(:target)])
X = permutedims(X)
y = permutedims(df_balanced.target)
data = CounterfactualData(X,y)
```

@@

```{julia}
df = CSV.read(joinpath(data_path, "raw/cs-training.csv"), DataFrame)
select!(df, Not([:Column1]))
rename!(df, :SeriousDlqin2yrs => :target)
mapcols!(x -> [ifelse(x_=="NA", missing, x_) for x_ in x], df)
dropmissing!(df)
mapcols!(x -> eltype(x) <: AbstractString ? parse.(Int, x) : x, df)
# # Features:
# X = Matrix(df[:,Not(:target)])
# dt = StatsBase.fit(ZScoreTransform, X, dims=1)
# StatsBase.transform!(dt, X)
# df = DataFrame(X,:auto)
# Target:
df.target .= map(y -> y == 0 ? 1 : 0, df.target)        # postive outcome = no delinquency
```

@@

One-hot encoding:

```{julia}
hot = OneHotEncoder()
mach = MLJBase.fit!(machine(hot, df_balanced))
df_balanced = MLJBase.transform(mach, df_balanced)
schema(df_balanced)
```

@@

```{julia}
X = Matrix(df_balanced[:,Not(:target)])
X = permutedims(X)
y = permutedims(df_balanced.target)
data = CounterfactualData(
    X, y;
    features_categorical = features_categorical
)
```

>>>>

```{julia}
df = CSV.read(joinpath(data_path, "raw/cal_housing.csv"), DataFrame)
# Target:
y = df.target
y = Float64.(y .>= median(y)); # binary target (positive outcome)
# Data:
df.target = y
```

@@

Feature transformation:

```{julia}
transformer = Standardizer(count=true)
mach = MLJBase.fit!(machine(transformer, df_balanced[:,Not(:target)]))
X = MLJBase.transform(mach, df_balanced[:,Not(:target)])
schema(X)
```

@@

```{julia}
X = Matrix(X)
X = permutedims(X)
y = permutedims(df_balanced.target)
data = CounterfactualData(X,y)
```

@@

```{julia}
df = CSV.read(joinpath(data_path, "raw/cs-training.csv"), DataFrame)
select!(df, Not([:Column1]))
rename!(df, :SeriousDlqin2yrs => :target)
mapcols!(x -> [ifelse(x_=="NA", missing, x_) for x_ in x], df)
dropmissing!(df)
mapcols!(x -> eltype(x) <: AbstractString ? parse.(Int, x) : x, df)
df.target .= map(y -> y == 0 ? 1 : 0, df.target)        # postive outcome = no delinquency
```

@@

Feature transformation:

```{julia}
transformer = Standardizer(count=true) |> ContinuousEncoder()
mach = MLJBase.fit!(machine(transformer, df_balanced[:,Not(:target)]))
X = MLJBase.transform(mach, df_balanced[:,Not(:target)])
schema(X)
```

@@

```{julia}
X = Matrix(X)
X = permutedims(X)
y = permutedims(df_balanced.target)
data = CounterfactualData(
    X, y;
    features_categorical = features_categorical
)
```

### 2022-12-21 docs/src/paper/experiments/_real_world.qmd
I just don't know why this isn't working for cat data

```{julia}
using CounterfactualExplanations.DataPreprocessing: unpack
bs = 500
function data_loader(data::CounterfactualData)
    X, y = unpack(data)
    data = Flux.DataLoader((X,y),batchsize=bs)
    return data
end
model_params = (batch_norm=false,n_hidden=64,n_layers=3,dropout=true,p_dropout=0.5)
```

>>>>

```{julia}
using CounterfactualExplanations.DataPreprocessing: unpack
bs = 500
function data_loader(data::CounterfactualData)
    X, y = unpack(data)
    data = Flux.DataLoader((X,y),batchsize=bs)
    return data
end
model_params = (batch_norm=false,n_hidden=64,n_layers=3,dropout=true,p_dropout=0.1)
```
